\thetitle

### 2021-05-21 writing/conclusion.tex
Respond to and add side notes

The work of~\citet{tgpk-dls-2018} suggests that, by intuition, programmers
prefer the run-time checking of Natural over other soundness methods. But of course,
the opinion of a random set of programmers does not mean that blame
assignment adds value. Similarly, researchers and language designers have
implicitly answered this question one way or another without evidence for the
blame-strategy dimension. The experiment presented in this paper provides some
justification for the programmers' leanings and helps language creators revisit
their decisions. Of course, the design choice remains a trade-off
along several dimensions while the presented experiment sheds light on
only one of them.

>>>>

The work of~\citet{tgpk-dls-2018} suggests that, by intuition, programmers
prefer the run-time checking of Natural over other soundness methods. But of course,
the opinion of a random set of programmers does not mean that blame
assignment adds value. Similarly, researchers and language designers have
implicitly answered this question one way or another without evidence for the
blame-strategy dimension. The experiment presented in this paper provides some
justification for the programmers' leanings
\ll{Does it really?}
and helps language creators revisit
their decisions. Of course, the design choice remains a trade-off
along several dimensions while the presented experiment sheds light on
only one of them.

### 2021-05-21 writing/rational.tex
Respond to and add side notes

Section~\ref{sec:why-rational} explains how a migratory type setting helps with
finding the source of an impedance mismatch. Roughly speaking, it encourages the
rational programmer to equip a module with types if it is blamed in an error
message. A sequence of such steps makes up a path in the
lattice of type migration~\citep{tfgnvf-popl-2016}. The lattice serves as the
universe \mf{what does this sentence really mean? what does it contribute?} for the definition modes of the rational programmer (see
sec.~\ref{sub:stuff}).

>>>>

Section~\ref{sec:why-rational} explains how a migratory type setting helps with
finding the source of an impedance mismatch. Roughly speaking, it encourages the
rational programmer to equip a module with types if it is blamed in an error
message. A sequence of such steps makes up a path in the
lattice of type migration~\citep{tfgnvf-popl-2016}. The lattice serves as the
common vocabulary for defining the modes of the rational programmer (see
sec.~\ref{sub:stuff}).
\mf{what does this sentence really mean? what does it contribute?}
\ll{Addressed}
